Chapter 2 Figures

### 2019-12-18 doc/figureFiles/figures.Rmd
changed error bars to 2SE

Fig1_Bv2_strain.male <- ggplot(strain.table.HQ[strain.table.HQ$sex == "male",], aes(y=mean_co, x=strain, color=strain))+facet_grid(~sex, scales = "free", space="free")+ 
  ylab("")+
  geom_point(size=3)+
  geom_errorbar(aes(ymin=mean_co-se, ymax=mean_co+se), width=.3)+
  ylim(c(18, 35))+
 scale_color_manual(values=colors_of_strains)+ 
  theme(legend.position="none",
  panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line=element_line(colour = "black"),
  axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+
#remove y labfor male 
  #Dom
  annotate("segment", x=.75, xend=3.6, y=19.5, yend=19.5, colour="black", size=1)+
  #Musc
  annotate("segment", x=3.9, xend=6.15, y=19.5, yend=19.5, colour="black", size=1)+
  #mol
  annotate("segment", x=6.5, xend=8.1, y=19.5, yend=19.5, colour="black", size=1)+
  #label
  annotate("text", x = c(2,5,7.15), #list of all x points 
           y = c(18.5,18.5, 18.5),

@@

# 2
Fig1_Bv2_strain.female <- ggplot(strain.table.HQ[strain.table.HQ$sex == "female",], aes(y=mean_co, x=strain, color=strain))+facet_grid(~sex, scales = "free", space="free")+ ylab("Average MLH1 Foci per Cell")+
  geom_point(size=3)+
  ylim(c(18, 35))+
  geom_errorbar(aes(ymin=mean_co-se, ymax=mean_co+se), width=.3) +
  scale_color_manual(values=colors_of_strains)+ 
  theme(legend.position="none", panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line = element_line(colour = "black"),
  axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  #segments
  annotate("segment", x=.75, xend=3.5,y=19.5, yend=19.5, colour="black", size=1)+
  #Musc
  annotate("segment", x=4, xend=6.5, y=19.5, yend=19.5, colour="black", size=1)+
#mol
 annotate("segment", x=7, xend=8.5, y=19.5, yend=19.5, colour="black", size=1)+
    #Cast
#  annotate("segment", x=4, xend=2, y=18, yend=18, colour="black", size=1)
#Labels
 annotate("text", x = c(2.25,5.6,6.5), #list of all x points 
           y = c(18.5,18.5,18.5),
           label = c("M. m. domesticus","M. m. musculus", "M.m.molossinus"),
           fontface = 'italic', hjust = 0.5, size=3.5)

@@

```{r Strain.fig.merge.v2, echo=FALSE}

fig1_B_v2  <- ggdraw() +
  draw_plot(Fig1_Bv2_strain.female, x=0, y = 0, width=.5, height=.97) +
  draw_plot(Fig1_Bv2_strain.male, x=.45, y=0, width=.5, height=.97) +

  draw_plot_label(label = c("A", "B"), size = 15,
                  x = c(0, .45), y = c(1, 1) )
fig1_B_v2
```

@@

## option 2, strain averages, more strains

>>>>

Fig1_Bv2_strain.male <- ggplot(strain.table.HQ[strain.table.HQ$sex == "male",], aes(y=mean_co, x=strain, color=strain))+facet_grid(~sex, scales = "free", space="free")+ 
  ylab("")+
  geom_point(size=3)+
  geom_errorbar(aes(ymin=mean_co-(se*2), ymax=mean_co+(se*2) ), width=.3)+
  ylim(c(18, 35))+
 scale_color_manual(values=colors_of_strains)+ 
  theme(legend.position="none",
  panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line=element_line(colour = "black"),
  axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+
#remove y labfor male 
  #Dom
  annotate("segment", x=.75, xend=3.6, y=19.5, yend=19.5, colour="black", size=1)+
  #Musc
  annotate("segment", x=3.9, xend=6.15, y=19.5, yend=19.5, colour="black", size=1)+
  #mol
  annotate("segment", x=6.5, xend=8.1, y=19.5, yend=19.5, colour="black", size=1)+
  #label
  annotate("text", x = c(2.2,5.9,6.1), #list of all x points 
           y = c(18.5,18.5, 33),

@@

# 2
Fig1_Bv2_strain.female <- ggplot(strain.table.HQ[strain.table.HQ$sex == "female",], aes(y=mean_co, x=strain, color=strain))+facet_grid(~sex, scales = "free", space="free")+ ylab("Average MLH1 Foci per Cell")+
  geom_point(size=3)+
  ylim(c(18, 35))+
  geom_errorbar(aes(ymin=mean_co-(se*2), ymax=mean_co+(se*2)), width=.3) +
  scale_color_manual(values=colors_of_strains)+ 
  theme(legend.position="none", panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  panel.background = element_blank(), axis.line = element_line(colour = "black"),
  axis.title.x=element_blank(),axis.text.x=element_blank(),axis.ticks.x=element_blank())+
  #segments
  annotate("segment", x=.75, xend=3.5,y=19.5, yend=19.5, colour="black", size=1)+
  #Musc
  annotate("segment", x=4, xend=6.5, y=19.5, yend=19.5, colour="black", size=1)+
#mol
 annotate("segment", x=7, xend=8.5, y=19.5, yend=19.5, colour="black", size=1)+
    #Cast
#  annotate("segment", x=4, xend=2, y=18, yend=18, colour="black", size=1)
#Labels
 annotate("text", x = c(2.25,5.9,6.1), #list of all x points 
           y = c(18.5,18.5,33),
           label = c("M. m. domesticus","M. m. musculus", "M.m.molossinus"),
           fontface = 'italic', hjust = 0.5, size=3.5)

@@

```{r Strain.fig.merge.v2, echo=FALSE}
fig1_B_v2  <- ggdraw() +
  draw_plot(Fig1_Bv2_strain.female, x=0, y = 0, width=.47, height=.97) +
  draw_plot(Fig1_Bv2_strain.male, x=.49, y=0, width=.48, height=.97) +

  draw_plot_label(label = c("A", "B"), size = 15,
                  x = c(0, .465), y = c(1, 1) )
fig1_B_v2
```

@@

## Option 2, strain averages, more strains
